Creative Destruction

### 2016-03-16 paper.tex
worked on intro of schumpeter and marx

\section{Introduction and Old Thoughts on Creative Destruction}
\subsection{Marx and Schumpter}
Creative destruction is an economic idea that refers to how new products, innovations, firms and regimes destroy old products, firms and regimes.
The idea has its roots in Marx, who questions why capitalism must destroy itself in order to exist.
Many have expanded on Marx ideas.
Most notably is Schumpeter in 1942 with his book \textit{Capitalism, Socialism and Democracy}.

Briefly, Schumpeter believes that a capitalistic economic system cannot be stationary; rather, it must be continuously in flux. 
The fundamental driver of the continuous change is new consumer good, new production methods, new markets, etc. 
The necessary new-ness of things creates ``the process of industrial mutation that incessantly revolutionizes the economic structure from within, incessantly destroying the old one, incessantly creating a new one'' \cite{wikipedia quote on schumpeter}.
Schumpter, like Marx, was skeptical of whether the creative destructive nature of capitalism was sustainable. 
Eventually, there could be too much destruction such that the system can no longer persist.

>>>>

\section{Introduction and Old Thoughts on Creative Destruction}
\subsection{Marx and Schumpter}
This first section will introduce creative destruction.
The idea has its roots in economics, and as such, this section will present creative destrucion in its economic form.
In effect, this section lacks philophical rigor.

Creative destruction is an economic idea that refers to how new products, firms and innovations destroy old products, firms and innovations.
Neoclassical economic theory, the most popular economic theory, is built on top of the idea of equilibrium.
Most simply, an economy has supply of things and demands of the same things. 
Supply and demand interact with each other, creating tension between economic processes.
The economy remains in flux until supply and demand reach a happy equilibrium.
At a happy equilibrium, supply and demand remain more or less constant until something disrupts the system.

The supply and demand theory has had strong explanatory power over the years, but it doesn't expalin one crucial observation: economies grow.
In a neoclassical economic framework, an economy reaches equilibrium and stabilizes.
Once an economy stabilizes, the only for it to grow is via exogenous inputs, for example, imperialism, increased supply of raw materials.

However, we observe that economies grow faster than the net exogenous inputs.
What could explain this?
Better worded: what explains endogenous growth in an economy?
After a close reading of Marx, Schumpeter came to the idea that innovation and entrepreneurship are the drivers of endogenous growth.
Innovation and entrepreneurship introduce new value to the economy that did not previously exist, contributing to an overall increase in social wealth.
However, Schumpeter also observed that new technologies (that is, the result of innovation)  and new firms often displace old technologies and old technologies.
The new technologies and new firms are better - specifically they have a lower margincal cost or are more desirable widgets - and the old technologies lose economic value and the old firms lose profits.

This the idea of creative destruction.
The old displaces new; there is not room for both of them.
Marx and Schumpeter had interesting concern: what if there is too much destruction by new technology such that society destroys itself.
The capitalist system is a cycle of creation and destruction, and it seems possible, on a theoretical level, that the destruction may overwhelm the construction, spelling distaster for society.
While on a social level this is hard to imagine, it is somewhat easier to fathom on technological level.

This paper will explore the idea of creative destruction and its philosopical implications on technology. 
To whet the appetite, a few questions that will be addressed are:
\begin{itemize}
    \item New technology technically does not ``destroy'' old technology; rather, it makes the old technology lose economic value. But, what effect does new technology have on old technology? Does it make it obsolete? Does the ``idea'' of the old technology change? Does the ``meaning'' of technology, which is contextual and socially constructed, changed due to a change in society or due to a change in technology? That question implies that technosphere, as one might call it, is distinct from society, which social constructs persuasively argue is not necessarily the case.
    \item asdf
\end{itemize}
